\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-24 papers/jfp/6-implementations.tex
Clean up the intro to S6

\section{Build systems, concretely}\label{sec-implementations}

\subsection{Build Systems \`a la Carte}\label{sec-design-space}

@@

With the information in this section we can build Table~\ref{tab-build-systems},
which tabulates combinations of the scheduling algorithm and the rebuilding
strategy, providing 12~possible build systems, 8~of which are inhabited
by existing build systems (we discuss these systems in~\S\ref{sec-background} and
\S\ref{sec-related-build}). Of the remaining 4~spots, all result in workable
build systems. The most interesting unfilled spot in the table is suspending
constructive traces, which would provide many benefits, and which we title
\Cloud \Shake and explore further in~\S\ref{sec-implementation-cloud}.
% (as we plan on extending \Shake to occupy that spot)

\subsection{Introduction}

In the previous sections we discussed the types of build systems, and how they
can be broken down into two main components: a scheduler and a rebuilder.
In this section we make this abstract distinction concrete, by
implementing a number of build systems as a composition of a scheduler
and a rebuilder.  Our design is expressed by these types (Fig.~\ref{fig-types}):

>>>>

\section{Build systems, concretely}\label{sec-implementations} \label{sec-design-space}

@@

In the previous sections we discussed the types of build systems, and how they
can be broken down into two main components: a scheduler (\S\ref{sec-scheduler})
and a rebuilder (\S\ref{sec-rebuilder}).
In this section we make this abstract distinction concrete, by
implementing a number of build systems as a composition of a scheduler
and a rebuilder. The result can be summarized in Table~\ref{tab-build-systems},
which tabulates combinations of the scheduling algorithm and the rebuilding
strategy, providing 12~possible build systems, 8~of which are inhabited
by existing build systems (we discuss these systems in~\S\ref{sec-background} and
\S\ref{sec-related-build}). Of the remaining 4~spots, all result in workable
build systems. The most interesting unfilled spot in the table is suspending
constructive traces, which would provide many benefits, and which we title
\Cloud \Shake and explore further in~\S\ref{sec-implementation-cloud}.
% (as we plan on extending \Shake to occupy that spot)

\subsection{Concrete Implementations}

We can define schedulers and rebuilders more concretely with the types (Fig.~\ref{fig-types}):
